A Dissection of Foregrounds in Epoch of Reionization Observations from the Murchison Widefield Array

### 2014-10-30 foreground_delay_spectrum_modeling.tex
Changed Josh's listed name
Added a citation to MWACS paper in eor.bib and changed the citation in text

%% Author list
\author{
%% Lead Authors
Nithyanandan~Thyagarajan\ASU\myemail,
Daniel~C.~Jacobs\ASU,
Judd~D.~Bowman\ASU,
N.~Barry\UW,
A.~P.~Beardsley\UW,
G.~Bernardi\SKASA$^,$\RU$^,$\CfA,
F.~Briggs\ANU$^,$\CAASTRO,
R.~J.~Cappallo\Haystack, 
P.~Carroll\UW,
B.~E.~Corey\Haystack, 
% A.~A.~Deshpande\RRI, 
A.~de~Oliveira--Costa\MIT,
J.~S.~Dillon\MIT,
D.~Emrich\Curtin,
% B.~M.~Gaensler\USydney$^,$\CAASTRO, 
A.~Ewall--Wice\MIT,
L.~Feng\MIT,
R.~Goeke\MIT,
L.~J.~Greenhill\CfA,
B.~J.~Hazelton\UW, 
J.~N.~Hewitt\MIT,
N.~Hurley--Walker\Curtin,
M.~Johnston-Hollitt\Victoria,
D.~L.~Kaplan\UWisc, 
J.~C.~Kasper\UMichigan$^,$\CfA, 
Han--Seek Kim\UMelbourne$^,$\CAASTRO,
P.~Kittiwisit\ASU,
E.~Kratzenberg\Haystack, 
E.~Lenc\USydney$^,$\CAASTRO,
J.~Line\UMelbourne$^,$\CAASTRO,
A.~Loeb\CfA,
C.~J.~Lonsdale\Haystack, 
M.~J.~Lynch\Curtin, 
B.~McKinley\UMelbourne$^,$\CAASTRO,
S.~R.~McWhirter\Haystack,
D.~A.~Mitchell\CASS$^,$\CAASTRO, 
M.~F.~Morales\UW, 
E.~Morgan\MIT, 
A.~R.~Neben\MIT,
D.~Oberoi\Tata, 
A.~R.~Offringa\ANU$^,$\CAASTRO, 
S.~M.~Ord\Curtin$^,$\CAASTRO,
Sourabh Paul\RRI,
B.~Pindor\UMelbourne$^,$\CAASTRO,
J.~C.~Pober\UW,
T.~Prabu\RRI, 
P.~Procopio\UMelbourne$^,$\CAASTRO,
J.~Riding\UMelbourne$^,$\CAASTRO,
A.~E.~E.~Rogers\Haystack, 
A.~Roshi\NRAO, 
N.~Udaya~Shankar\RRI, 
Shiv~K.~Sethi\RRI,
K.~S.~Srivani\RRI, 
R.~Subrahmanyan\RRI$^,$\CAASTRO, 
I.~S.~Sullivan\UW,
M.~Tegmark\MIT,
S.~J.~Tingay\Curtin$^,$\CAASTRO, 
C.~M.~Trott\Curtin$^,$\CAASTRO,
M.~Waterson\Curtin$^,$\ANU,
R.~B.~Wayth\Curtin$^,$\CAASTRO, 
R.~L.~Webster\UMelbourne$^,$\CAASTRO, 
A.~R.~Whitney\Haystack, 
A.~Williams\Curtin, 
C.~L.~Williams\MIT,
C.~Wu\UWA,
J.~S.~B.~Wyithe\UMelbourne$^,$\CAASTRO
}

@@

The data are flagged\footnote{\url{http://sourceforge.net/p/aoflagger}} for interference \citep{off10,off12}, removing 3\% of the data and averaged in time  and frequency from the raw 0.5~s, 40~kHz to 2s, 80~kHz. These data are then calibrated to a simulation of the sky containing 2420 point--like objects selected from the MWA Commissioning Survey (MWACS; Hurley-Walker et al. 2014, submitted). % MWACS was compiled using observations taken with subsets of the array during the final buildout and commissioning;
It has a flux density limit of 25~mJy and a declination range of -12\arcdeg~ to -40\arcdeg~ evenly covering the field of view of the observations reported here. The objects used in calibration are selected to lie inside the 5\% contour of the primary lobe of the tile power--pattern. The calibration algorithm -- based on forward modeling software by \citet{sul12} and the calibration method described by \citet{sal14} -- computes complex gain solutions per channel per antenna averaged to two minute intervals. The solutions are fairly low signal--to--noise so we iteratively average along the antenna and frequency dimensions to capture the relatively independent passband and antenna--to--antenna variation. First, we average the channel gains over all antennas to obtain a high signal--to--noise measurement of the bandpass. After applying this single passband, we do a second round of calibration and fit second and first order polynomials for amplitude and phase respectively for each antenna. This flattens any residual variation in bandpass and removes small phase slopes due to variations in cable delay. Finally, we fit for an additional phase known to be caused by small reflections in subset of cables.

>>>>

%% Author list
\author{
%% Lead Authors
Nithyanandan~Thyagarajan\ASU\myemail,
Daniel~C.~Jacobs\ASU,
Judd~D.~Bowman\ASU,
N.~Barry\UW,
A.~P.~Beardsley\UW,
G.~Bernardi\SKASA$^,$\RU$^,$\CfA,
F.~Briggs\ANU$^,$\CAASTRO,
R.~J.~Cappallo\Haystack, 
P.~Carroll\UW,
B.~E.~Corey\Haystack, 
% A.~A.~Deshpande\RRI, 
A.~de~Oliveira-Costa\MIT,
Joshua~S.~Dillon\MIT,
D.~Emrich\Curtin,
% B.~M.~Gaensler\USydney$^,$\CAASTRO, 
A.~Ewall-Wice\MIT,
L.~Feng\MIT,
R.~Goeke\MIT,
L.~J.~Greenhill\CfA,
B.~J.~Hazelton\UW, 
J.~N.~Hewitt\MIT,
N.~Hurley-Walker\Curtin,
M.~Johnston-Hollitt\Victoria,
D.~L.~Kaplan\UWisc, 
J.~C.~Kasper\UMichigan$^,$\CfA, 
Han-Seek Kim\UMelbourne$^,$\CAASTRO,
P.~Kittiwisit\ASU,
E.~Kratzenberg\Haystack, 
E.~Lenc\USydney$^,$\CAASTRO,
J.~Line\UMelbourne$^,$\CAASTRO,
A.~Loeb\CfA,
C.~J.~Lonsdale\Haystack, 
M.~J.~Lynch\Curtin, 
B.~McKinley\UMelbourne$^,$\CAASTRO,
S.~R.~McWhirter\Haystack,
D.~A.~Mitchell\CASS$^,$\CAASTRO, 
M.~F.~Morales\UW, 
E.~Morgan\MIT, 
A.~R.~Neben\MIT,
D.~Oberoi\Tata, 
A.~R.~Offringa\ANU$^,$\CAASTRO, 
S.~M.~Ord\Curtin$^,$\CAASTRO,
Sourabh Paul\RRI,
B.~Pindor\UMelbourne$^,$\CAASTRO,
J.~C.~Pober\UW,
T.~Prabu\RRI, 
P.~Procopio\UMelbourne$^,$\CAASTRO,
J.~Riding\UMelbourne$^,$\CAASTRO,
A.~E.~E.~Rogers\Haystack, 
A.~Roshi\NRAO, 
N.~Udaya~Shankar\RRI, 
Shiv~K.~Sethi\RRI,
K.~S.~Srivani\RRI, 
R.~Subrahmanyan\RRI$^,$\CAASTRO, 
I.~S.~Sullivan\UW,
M.~Tegmark\MIT,
S.~J.~Tingay\Curtin$^,$\CAASTRO, 
C.~M.~Trott\Curtin$^,$\CAASTRO,
M.~Waterson\Curtin$^,$\ANU,
R.~B.~Wayth\Curtin$^,$\CAASTRO, 
R.~L.~Webster\UMelbourne$^,$\CAASTRO, 
A.~R.~Whitney\Haystack, 
A.~Williams\Curtin, 
C.~L.~Williams\MIT,
C.~Wu\UWA,
J.~S.~B.~Wyithe\UMelbourne$^,$\CAASTRO
}

@@

The data are flagged\footnote{\url{http://sourceforge.net/p/aoflagger}} for interference \citep{off10,off12}, removing 3\% of the data and averaged in time  and frequency from the raw 0.5~s, 40~kHz to 2s, 80~kHz. These data are then calibrated to a simulation of the sky containing 2420 point--like objects selected from the MWA Commissioning Survey \citep[MWACS;][]{hur14}. % MWACS was compiled using observations taken with subsets of the array during the final buildout and commissioning;
It has a flux density limit of 25~mJy and a declination range of -12\arcdeg~ to -40\arcdeg~ evenly covering the field of view of the observations reported here. The objects used in calibration are selected to lie inside the 5\% contour of the primary lobe of the tile power--pattern. The calibration algorithm -- based on forward modeling software by \citet{sul12} and the calibration method described by \citet{sal14} -- computes complex gain solutions per channel per antenna averaged to two minute intervals. The solutions are fairly low signal--to--noise so we iteratively average along the antenna and frequency dimensions to capture the relatively independent passband and antenna--to--antenna variation. First, we average the channel gains over all antennas to obtain a high signal--to--noise measurement of the bandpass. After applying this single passband, we do a second round of calibration and fit second and first order polynomials for amplitude and phase respectively for each antenna. This flattens any residual variation in bandpass and removes small phase slopes due to variations in cable delay. Finally, we fit for an additional phase known to be caused by small reflections in subset of cables.
